Incentivizing Exploration with Unbiased History

### 2018-10-29 llevel-overview.tex
llevel in intro

 \draw [rounded corners=3mm, line width=1mm, red](-0.2,4.8)--(2.2,4.8)--(2.2,6.2)--(-0.2,6.2)--cycle;
  \draw [rounded corners=3mm, line width=1mm, red](5.8,4.8)--(8.2,4.8)--(8.2,6.2)--(5.8,6.2)--cycle;
\end{tikzpicture}
\caption{Connectiing structures between levels for the $L$-level policy.}
\label{fig:llevel-connecting}
\end{figure}
\xhdr{Additional groups for boundary cases.} In our 3-level policy, recall the medium gap case (Lemma \ref{3levelmedium}) is the boundary case when the gap $|\mu_1-\mu_2|$ is $\Omega\left(\sqrt{\frac{1}{T_1}}\right)$ and $O\left(\sqrt{\frac{\log(T)}{T_1}}\right)$. In this case, the gap is not large enough to conclude that with high probability agents in both the second level and the third level all pull the best arm. The gap is also not small enough to conclude that with high probability both arms are explored enough times in the second level.

In our $L$-level policy, we resolve this problem by introducing an additional type of groups: $\Gamma$-groups and we call the original groups $G$-groups.

>>>>

 \draw [rounded corners=3mm, line width=1mm, red](-0.2,4.8)--(2.2,4.8)--(2.2,6.2)--(-0.2,6.2)--cycle;
  \draw [rounded corners=3mm, line width=1mm, red](5.8,4.8)--(8.2,4.8)--(8.2,6.2)--(5.8,6.2)--cycle;
\end{tikzpicture}
\caption{Connectiing structures between levels for the $L$-level policy.}
\label{fig:llevel-connecting}
\end{figure}
\xhdr{Additional groups for boundary cases.} Recall in our 3-level policy, the medium gap case (Lemma \ref{3levelmedium}) is the boundary case when the gap $|\mu_1-\mu_2|$ is $\Omega\left(\sqrt{\frac{1}{T_1}}\right)$ and $O\left(\sqrt{\frac{\log(T)}{T_1}}\right)$. In this case, the gap is not large enough to conclude that with high probability agents in both the second level and the third level all pull the best arm. The gap is also not small enough to conclude that with high probability both arms are explored enough times in the second level. We need to worry about the situation in which the sub-optimal arm does not get pulled enough times in the first two levels and some agents in the third level may pull the sub-optimal arm. Such situation is naturally ruled out in our 3-level policy for the following reason. Agents in the third level observe the history of the entire first level while agents in the second level only observes the history of a single first-level group. For each arm, even if it is not pulled at all in the second level, its empirical mean concentrates closer to its actual mean in the history observed by a third-level agent than the one observed by a second-level agent. Therefore, although the gap in the medium gap case is just not large enough for agents in the second level to all pull the best arm, it is large enough for agents in the third level to all pull the best arm.

When we extend the 3-level policy to an $L$-level policy, we have such boundary case for each intermediate level. Moreover, the worry mentioned above does not get naturally resolved as in some of these boundary cases, the ratios between the upper and lower bounds of the gap rise from $\Theta(\sqrt{\log(T)})$ to $\Theta(\log(T))$. The reason for such rise is that, except the first level, we don't have good enough guarantee of the number of pulls of each arm. For example, in Figure \ref{fig:llevel-connecting}, when we talk about having enough arm $a$ pulls in the history observed by agents in $G_{l,1,1}$, it could be that just only agents in group $G_{l-1,1,1}$ are pulling arm $a$ and it could also be that most agents in groups $G_{l-1,1,1},G_{l-1,1,2},...,G_{l-1,1,S}$ are pulling arm $a$. Therefore we only get a $S=\Theta(\log(T))$ multiplicative factor estimate of the number of arm $a$ pulls and this finally makes the boundary cases harder to deal with.

In our $L$-level policy, after understanding the boundary cases well, we resolve this problem by introducing an additional type of groups: $\Gamma$-groups. For each $l \in [L], u,v \in [S]$, we create a $\Gamma$-group $\Gamma_{l,u,v}$. Agents in $\Gamma_{l,u,v}$ observe the same history as agents in $G_{l,u,v}$ and the number of agents in $\Gamma_{l,u,v}$ is $\Theta(\log(T)$ times the number of agents in $G_{l,u,v}$. The history of $\Gamma$ groups in level $l$ is not sent to agents in level $l+1$ but higher levels. Consider the boundary case in which we can not say anything about the $l+1$ level agents' pulls. The new construction makes sure that agents in levels higher than $l+1$ get enough pulls of each arm and all pull the best arm in this boundary case.
